\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-14 doc/publications/plos16/plos16.tex
new p-value

As shown in Fig~\ref{figure:ranksumtest}, the known genes are ranked significantly higher than variants from other
locations in the genome (Mann-Whitney U, $p=1.3\times10^{-07}$), supporting our hypothesis that biologically relevant
features are contributing more information to our classification model.

>>>>

As shown in Fig~\ref{figure:ranksumtest}, the known genes are ranked significantly higher than variants from other
locations in the genome (Mann-Whitney U, $p=9.71\times10^{-15}$), supporting our hypothesis that biologically relevant
features are contributing more information to our classification model.
